Graphical Tests for Power Comparison of Competing Designs

### 2012-03-31 conclusions.tex
conclusions

\section{Conclusions}~\label{conclusions}

>>>>

% !TEX root = comparison.tex
\section{Conclusions}~\label{conclusions}
Lineup charts allow us to assess and quantify the strength of a visual finding. In this paper we introduce the concept of  the power of a lineup, and show its use as a measure to evaluate competing designs. 
Power of a lineup can be modeled in a logistic regression model with subject-specific random effects, if observers were exposed and provided feedback to multiple lineups.

We describe two MTurk studies evaluating different designs.
